Zaca Fire Type Conversion

### 2020-08-04 Model Data Sheets and Code/Zaca MCF Mortality Model Results.Rmd
minor changes

1. Can the mcf model distinguish between type conversion and the other mortality types? 
  - so far, no! so variable importance is not meaningful for that model

2. Which variables contribute to type conversion of MCFs?

3. How well does rdnbr compare to manual estimates of mortality?

4. How does using rdnbr and manually derived mortality compare as a response variable?

5. Which variables contribute to high/low mortality? high/low rdnbr?

5. Does conifer type contribute to different variable importances?

>>>>

1. Can the mcf model distinguish between type conversion and the other mortality types? 
    yes, if we use ALE plots

2. Which variables contribute to type conversion of MCFs and pico?

3. How well does rdnbr compare to manual estimates of mortality? 
    high rdnbr matches up very well with high mortality. There is less of a match up between moderate, low,      and no mortality with the corresponding rdnbr severity levels.

4. How does using rdnbr and manually derived mortality compare as a response variable?
    this would be a better question for the big cone model

5. Which variables contribute to high/low/type conversion rdnbr? Is there a distinguishable difference between values of the explanatory variables for high/type conversion levels of rdnbr?

6. Does conifer type contribute to different variable importances?
